---
title: "EGG Brain Wave of Confusion"
output: github_document
---

Remove subjectID and VideoID
Reorder demographic feature to the first columns.
```{r}
eeg = eeg[c("age", "ethnicity", "gender", "Attention", "Meditation","Raw", "Delta", "Theta", "Alpha1", "Alpha2", "Beta1", "Beta2", "Gamma1", "Gamma2", "predefined_label","Self_defined_label")]
sapply(eeg, class)
```

get plots of relations among all features and target
```{r}
plot(eeg)
summary(eeg)
pairs(eeg,col=eeg$predefined_label)
hist(eeg$Gamma1)
```

```{r}
eeg.fit = glm(predefined_label~., data = eeg, family = 'binomial')
summary(eeg.fit)
eeg.fit1 = glm(predefined_label~age+ethnicity+Raw+Beta1+Beta2+Gamma2, data = eeg, family = 'binomial')
summary(eeg.fit1)
eeg.fit2 = glm(predefined_label~age+ethnicity+Raw+Beta1*Beta2+Gamma2, data = eeg, family = 'binomial')
summary(eeg.fit2)
```

```{r}
library(dplyr)
library(caret)
train = sample_frac(eeg, 0.75)
num = as.numeric(rownames(train))
test = eeg[-num,]
train.fit = knn3(predefined_label~age+ethnicity+Raw+Beta1+Beta2+Gamma2, data = eeg)
summary(train.fit)
probs = predict(train.fit, test)
pred = rep(0, length(probs))
pred[probs>=0.5] = 1
mean(pred != test$predefined_label)
```

use glm to train and test data 
```{r}
#set.seed(1)
library(MASS)
data = eeg
apply(data,2,function(x) sum(is.na(x)))
index = sample(1:nrow(data),round(0.75*nrow(data)))
train = data[index,]
test = data[-index,]
lm.fit = glm(predefined_label~., data=train)
summary(lm.fit)
pr.lm = predict(lm.fit,test)
pred = rep(0, length(pr.lm))
pred[pr.lm>=0.5] = 1
mean(pred != test$predefined_label)
MSE.lm = sum((pr.lm - test$predefined_label)^2)/nrow(test)
MSE.lm
```


```{r}
data = data[6:15]
maxs = apply(data,2,max)
mins = apply(data,2,min)
scaled = as.data.frame(scale(data, center = mins, scale = maxs - mins))
train_ = scaled[index,]
test_ = scaled[-index,]
library(neuralnet)
n = names(train_)
f = as.formula(paste("predefined_label ~", paste(n[!n %in% "predefined_label"], collapse = " + ")))
nn = neuralnet(f,data=train_,hidden = 1)
debugonce(nn) 
plot(nn)
resu = compute(nn, test_[,1:9])
pred = rep(0, length(resu))
pred[resu>=0.5] = 1
mean(pred != test$predefined_label)
```

```{r}
library("e1071")
train = sample_frac(eeg, 0.75)
num = as.numeric(rownames(train))
test = eeg[-num,]
train.fit = svm(predefined_label~., data = train)
summary(train.fit)
probs = predict(train.fit, test)
pred = rep(0, length(probs))
pred[probs>=0.5] = 1
mean(pred != test$predefined_label)
#66.66%
```

```{r}
# Read EEG data from CSV
eeg_raw = read.csv("EEG.csv")
dim(eeg_raw)
names(eeg_raw)
# Remove SubjectID and VideoID
eeg_noID = data.frame(eeg_raw[,-c(1,2,14)])
eeg_noIDsub6 = eeg_raw[eeg_raw$SubjectID != 6,]
eeg_noIDsub6 = data.frame(eeg_noIDsub6[,-c(1,2,14)])
# Correlation Analysis
cor(eeg_noID)
```

#data normalization:Standardize data columns
```{r}
library("e1071")
library(caret)
library(dplyr)
library(class)
set.seed(123)
preObj = preProcess(eeg_noID[,-12], method=c("BoxCox"))
dataNom = predict(preObj, eeg_noID)
```

#data normalization without subject6
```{r}
library("e1071")
library(caret)
library(dplyr)
library(class)
set.seed(123)
preObj = preProcess(eeg_noIDsub6[,-12], method=c("BoxCox"))
dataNom = predict(preObj, eeg_noIDsub6)
```

# No dataNorm
```{r}
set.seed(3286)
random_vector = runif(length(eeg_noIDsub6$SelfDefinedConfusion))
train = random_vector < 0.7
test = !train
train_num = sum(train == TRUE)
test_num = sum(train == FALSE)
train_set_noNor = eeg_noID[train,]
test_set_noNor = eeg_noID[test,]
```


# Randomly separate data into train and test.
```{r}
set.seed(3286)
random_vector = runif(length(dataNom$SelfDefinedConfusion))
train = random_vector < 0.7
test = !train
train_num = sum(train == TRUE)
test_num = sum(train == FALSE)
train_set = dataNom[train,]
test_set = dataNom[test,]
```

# Do Logistic Regression
```{r}
glm.fit = glm(SelfDefinedConfusion~., data = train_set_noNor, family = "binomial")
summary(glm.fit)
probs = predict(glm.fit, test_set_noNor, type = "response")
pred = rep(0, length(probs))
pred[probs>0.5] = 1
mean(pred == test_set_noNor$SelfDefinedConfusion)
# 60.2%
# 60.0% without sub6
```

# Do SVM
```{r}
svm.fit = svm(SelfDefinedConfusion~., data = train_set_noNor)
plot(svm.fit)
summary(svm.fit)
probs = predict(svm.fit, test_set_noNor)
pred = rep(0, length(probs))
pred[probs>0.5] = 1
mean(pred == test_set_noNor$SelfDefinedConfusion)
# 64.1%
# 64.0% without sub6
```

# RandomForest
```{r}
#install.packages('randomForest', repos="http://cran.r-project.org")
require(randomForest)
require(MASS)
set.seed(101)
#tree.fit = tree(SelfDefinedConfusion~., data = train_set)
rf.fit = randomForest(SelfDefinedConfusion~., data = train_set_noNor, ntree = 400)
plot(rf.fit)
summary(rf.fit)
probs = predict(rf.fit, test_set_noNor)
pred = rep(0, length(probs))
pred[probs>0.5] = 1
mean(pred == test_set_noNor$SelfDefinedConfusion)
#67.4%
#67.0% without sub6
```

# Boosting
```{r}
#install.packages('gbm', repos="http://cran.r-project.org")
require(gbm)
boost.eeg=gbm(SelfDefinedConfusion~.,data=train_set_noNor,distribution="gaussian",n.trees=6000,shrinkage=0.01,interaction.depth=4)
summary(boost.eeg)
n.trees=seq(from=100,to=10000,by=100)
predmat=predict(boost.eeg,newdata=test_set_noNor,n.trees=6000)
pred = rep(0, length(predmat))
pred[predmat>0.5] = 1
mean(pred == test_set_noNor$SelfDefinedConfusion)
# 65.4%
# 66.4% without sub6
dim(predmat)
berr=with(test_set,apply( (predmat-SelfDefinedConfusion)^2,2,mean))
plot(n.trees,berr,pch=19,ylab="Mean Squared Error", xlab="# Trees",main="Boosting Test Error")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
